On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-28 Manuscript/manuscript.tex
Small Manuscript Update

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\delta$, the difference between a point estimate and
$\bar\theta_n^{(b)}$. For $b \in \{1, \ldots, B\}$, we can obtain a
$\delta^{(b)}$ based on the $b$th bootstrap point estimate. Let
$\delta_{\alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\delta^{(1)}, \ldots,  \delta^{(B)}\}$.  
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2}, \quad
\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
\]
This CI is necessarily centered around the point estimator $\hat\theta_n$ and
is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

Based on Figure~\ref{fig:mu}, 
Student's $t$ CIs appear to have the greatest coverage rates with respect 
to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover $\mu$
for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, CBP, Centered, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, CBP, Centered, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.

@@

Based on Figure~\ref{fig:phi}, 
Percentile, CBP, $BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. When $\phi = -0.4$, Standard and Centered CIs 
recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
$\phi = -0.2$, Standard and Centered CIs recover $\phi$ at $n = 800$ and 
$n = 1600$, 
although they undercover $\phi$ at $n = 3600$, indicating that 
perhaps a larger $n$ is needed if these CIs are uses. However,
Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
$\phi = 0$, Standard and Centered CIs recover $\phi$ relatively comfortably 
at $n = 3200$, and 
$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
and Centered CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
800$ is large enough for Standard and Centered CIs. Student's $t$ CIs either
recover or over-cover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma$,
$BC_a$ should not be used, and Student's $t$ again has the greatest coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 3200$ may be necessary for block bootstrap interval estimation of
$\sigma$. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Centered and Standard CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 800$ is large enough to
recover $\phi$ when using the Student's $t$ method.

@@

Again, this analysis \eds{what?} \mc{addressed} relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the five types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for Standard, Student's $t$, and Centered CIs, whereas 
Percentile, CBP, $BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
increased. The Percentile CI's coverage deterioration can be attributed to
bias that is not corrected as $n$ increases. Specifically, as $n$ increases, 
the width of the CI decreases, but because the Percentile CI
underestimates $\phi$, the coverage decreases. The $BC_a$ CI does seem to correct the bias, but the acceleration factor seems to fail, as the width of the CI
seems to be inconsistent.

>>>>

\paragraph{Proposed Method CI}
Our Proposed Method CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)$ CI using our Proposed Method is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \hat{bias}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \hat{bias}).
\]
This CI is necessarily centered around .... and
is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

Based on Figure~\ref{fig:mu}, 
Student's $t$ CIs appear to have the greatest coverage rates with respect 
to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover $\mu$
for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, CBP, Proposed Method, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, CBP, Proposed Method, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.

@@

Based on Figure~\ref{fig:phi}, 
Percentile, CBP, $BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. When $\phi = -0.4$, Standard and Proposed Method CIs 
recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
$\phi = -0.2$, Standard and Proposed Method CIs recover $\phi$ at $n = 800$ and 
$n = 1600$, 
although they undercover $\phi$ at $n = 3600$, indicating that 
perhaps a larger $n$ is needed if these CIs are uses. However,
Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively comfortably 
at $n = 3200$, and 
$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
and Proposed Method CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
800$ is large enough for Standard and Proposed Method CIs. Student's $t$ CIs either
recover or over-cover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma$,
$BC_a$ should not be used, and Student's $t$ again has the greatest coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 3200$ may be necessary for block bootstrap interval estimation of
$\sigma$. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 800$ is large enough to
recover $\phi$ when using the Student's $t$ method.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/pct}
  \caption{}
  \label{fig:pct}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/prop}
  \caption{}
  \label{fig:prop}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/bc}
  \caption{}
  \label{fig:bc}
\end{figure}

@@

Again, this analysis \eds{what?} \mc{addressed} relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the five types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for Standard, Student's $t$, and Proposed Method CIs, whereas 
Percentile, CBP, $BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
increased. The Percentile CI's coverage deterioration can be attributed to
bias that is not corrected as $n$ increases. Specifically, as $n$ increases, 
the width of the CI decreases, but because the Percentile CI
underestimates $\phi$, the coverage decreases. The $BC_a$ CI does seem to correct the bias, but the acceleration factor seems to fail, as the width of the CI
seems to be inconsistent.
